### 2015-09-14 Projects/DelCo_2012/Report/DelCo_2012.tex
update report and plotting script

\headerC{
\flushright{
Daniel Madrzykowski \\
Keith M. Stakes \\
Craig G. Weinschenk \\
{\em Fire Research Division \\
Engineering Laboratory} \\

@@

\large
\flushright{\bf National Institute of Standards and Technology Technical Note XXXX \\
Natl.~Inst.~Stand.~Technol.~Tech.~Note~XX, \pageref{LastPage} pages (August 2014) \\
% http://dx.doi.org/10.6028/NIST.TN.XXXX \\
CODEN: NTNOEF }

@@

% \begin{sidewaystable}[!ht]
% 	\centering
% 	\caption{Temperature Comparison}
% 	\begin{tabular}{ll}
% 		\hline\noalign{\smallskip}
% 		Temperature				 & Response		\\
% 		\noalign{\smallskip}\hline\noalign{\smallskip}
% 		37 deg C (98.6 deg F)    &  Normal human oral/body temperature      \\
% 		44 deg C (111 deg F)   	 & Human skin begins to feel pain     \\
% 		48 deg C (118 deg F) 	 & Human skin receives a first degree burn injury      \\
% 		55 deg C (131 deg F)     & Human skin receives a second degree burn injury    \\
% 		62 deg C (140 deg F)     & A phase where burned human tissue becomes numb    \\
% 		72 deg C (162 deg F)     & Human skin instantly destroyed     \\
% 		100 deg C (212 deg F)    & Water boils and produces steam    \\
% 		140 deg C (284 deg F)    & Glass transition temperature of polycarbonate (SCBA Facepieces)      \\
% 		230 deg C (446 deg F)    & Melting temperature of polycarbonate (SCBA Facepieces)    \\
% 		250 deg C (482 deg F)    & Charring of natural cotton begins     \\
% 		>300 deg C (>572 deg F)  & Charring of modern protective clothing fabrics begins    \\
% 		>600 deg C (>1112 deg F) & Temperatures inside a post-flashover compartment fire     \\
% 		\noalign{\smallskip}\hline
% 	\end{tabular}
% 	\label{tab:Temperature_Comparison}
% \end{sidewaystable}

% \begin{sidewaystable}[!ht]
% 	\centering
% 	\caption{Heat Flux Comparison}
% 	\begin{tabular}{ll}
% 		\hline\noalign{\smallskip}
% 		Heat Flux	  				   & Response		\\
% 		\noalign{\smallskip}\hline\noalign{\smallskip}
% 		1 kW/m\textsuperscript{2}      & Sunny day      \\
% 		2.5 kW/m\textsuperscript{2}    & Typical firefighter exposure     \\
% 		3-5 kW/m\textsuperscript{2}    & Pain to skin within seconds      \\
% 		20 kW/m\textsuperscript{2}     & Threshold flux to floor at flashover onset    \\
% 		84 kW/m\textsuperscript{2}     & Thermal Protection Performance (TPP) test    \\
% 		60-200 kW/m\textsuperscript{2} & Flames over surface     \\
% 		\noalign{\smallskip}\hline
% 	\end{tabular}
% 	\label{tab:Heat_Flux_Comparison}
% \end{sidewaystable}

@@

BB6        &   120              & 21            & Water  &  30$^{\circ}$ fog   & 15                 &          \\
BB7        &   118              & 21            & Water  &  30$^{\circ}$ fog   & 15                 &          \\
BB8        &   119              & 22            & Water  &  30$^{\circ}$ fog   & 17                 &          \\
BB9        &   120              & 24            & Water  &  30$^{\circ}$ fog   & 17~1/2             &          \\
BB10       &   127              & 20            & Water  &  Solid 7/8~in slug  & 12~1/2             &          \\
BB11       &   120              & 22            & Water  &  Solid 7/8~in slug  & 11~1/2             &          \\

@@

BB16       &   120 / 60cfm      &               & CAF    &  30$^{\circ}$ fog   & 15                 &          \\

@@

BB19       &   120 / 60cfm      & 15            & CAF    &  30$^{\circ}$ fog   & 15                 &          \\
BB20       &   120 / 60cfm      &               & CAF    &  30$^{\circ}$ fog   & 17                 &          \\

@@

CS5        &   118              & 22            & Water  &  30$^{\circ}$ fog   &                    &          \\
CS6        &   118              & 19            & Water  &  30$^{\circ}$ fog   &                    &          \\
CS7        &   125              & 16            & Water  &  Solid 7/8~in slug  &                    &          \\
CS7.2      &   120              & 17            & Water  &  Solid 7/8~in slug  & 18                 &          \\
CS8        &   116              & 15            & Water  &  30$^{\circ}$ fog   &                    &          \\
CS9        &   116              & 16            & Water  &  30$^{\circ}$ fog   &                    &          \\

@@

After weighing each of the bins the mass of water (kg) in each bin was plotted by position to visualize the spray distribution. Figure~\ref{fig:Burn_Building_Test_1} shows that with a straight stream positioned {\bf here} the majority of the water accumulated along the north and east walls of the gas cooling room within the burn building (cf. Fig.~\ref{fig:Delaware_County,_PA_Burn_Building_Layout}). Figure~\ref{fig:Burn_Building_Test_7} shows difference a fog stream as the distrubtion of water is far more dispered around the gas cooling room. The remainder of the burn building spray density figures are included in Appnedix~\ref{app:spray_density}.

@@

\section{Fire Suppression}
\label{sec:Fire_Suppression}
Several of the tests used a wood fuel load comprised of pallets and the remaining tests used a more realistic fuel load comprised of common household furnishings to include wooden wall paneling, two sofas, two overstuffed chairs, carpet, and padding.  The burn room was located to the rear of the single story structures and the available ventilation was both through the front doorway and from a rear window, dependent on the test in question.  The fires were intended to replicate room and contents fires typically seen within residential structures.  The hose lines were pre-deployed with fixed nozzles set in two locations.  One in the hallway on the approach to the burn room (hallway nozzle), and one just inside the burn room to the right side of the hallway (room nozzle). The hallway nozzle was intended to simulate a crew advancing into a structure towards the burn room. Suppression from this location would be in the form of gas cooling as the stream was not aimed at the seat of the fire, representing an indirect interior attack. The room nozzle was intended to simulate a crew which had advanced into a structure, entered the fire room, positioned just to the side of the entry door, and began suppression on the seat of the fire.  This position represented a direct interior attack.

\begin{sidewaystable}[!ht]
	\centering
	\caption{Test Descriptions}
	\begin{tabular}{lllll}
		\hline\noalign{\smallskip}
		Test		& Agent		& Stream				& Flow Rate			& Comments \\
		\noalign{\smallskip}\hline\noalign{\smallskip}
		1 (FSE1)    &  CAF      &  30 deg Fog  			&  120 gpm/60 cfm   &	Furniture Fuel Package  \\
		2 (FSW2)   	& Water     &  30 deg Fog  			&  120 gpm    		&	Furniture Fuel Package	\\
		3 (FSW3) 	&  CAF      &  7/8" Smooth Bore  	&  120 gpm/60 cfm   &	Furniture Fuel Package  \\
		4 (FSE4)    &  Water    &  7/8" Smooth Bore  	&  120 gpm    		&	Furniture Fuel Package	\\
		5 (FSE5)    &  Water    &  30 deg Fog  			&  120 gpm    		&	Furniture Fuel Package	\\
		6 (FSW6)    &  CAF      &  30 deg Fog  			&  120 gpm/60 cfm   &	Furniture Fuel Package  \\
		7 (FSW7)    &  Water    &  30 deg Fog  			&  120 gpm    		&	Furniture Fuel Package	\\
		8 (FSE8)    &  CAF      &  30 deg Fog  			&  120 gpm/60 cfm   &	Furniture Fuel Package  \\
		9 (Attic 1) &  Water    &  Straight Stream  	&  120 gpm    		&	Furniture Fuel Package	\\
		10 (Attic 2)&  CAF      &  Straight Stream  	&  120 gpm/60 cfm   &	Furniture Fuel Package  \\
		11 (FSE1)   &  Water    &  30 deg Fog  			&  120 gpm   		&	Wood Fuel Package, Panel Window	 \\
		12 (FSW1)   &  CAF      &  30 deg Fog  			&  120 gpm/60 cfm   &	Wood Fuel Package, Panel Window  \\
		13 (FSE2)   &  Water    &  30 deg Fog  			&  120 gpm    		&	Wood Fuel Package, Panel Window  \\
		14 (FSW2)   &  CAF      &  30 deg Fog  			&  120 gpm/60 cfm   &	Wood Fuel Package, Panel Window  \\
		\noalign{\smallskip}\hline
	\end{tabular}
	\label{tab:Test_Descriptions}
\end{sidewaystable}

\begin{sidewaystable}[!ht]
	\centering
	\caption{Nozzle Activation Times}
	\begin{tabular}{lllllll}
		\hline\noalign{\smallskip}
		Test		& Agent		& Stream				& Nozzle 1 Activation	& Nozzle 1 Shut Off		& Nozzle 2 Activation	& Nozzle 2 Shut Off \\
		\noalign{\smallskip}\hline\noalign{\smallskip}
		1 (FSE1)    &  CAF      &  30 deg Fog  	    	& 233 					& 248					& 269					& 284					\\
		2 (FSW2)   	& Water     &  30 deg Fog  	    	& 235					& 250					& 272					& 287					\\
		3 (FSW3) 	&  CAF      &  7/8" Smooth Bore     & 228					& 243 					& 255					& 270					\\
		4 (FSE4)    &  Water    &  7/8" Smooth Bore     & 233					& 248					& 268					& 283					\\
		5 (FSE5)    &  Water    &  30 deg Fog  	    	& 232					& 247					& 257					& 272					\\
		6 (FSW6)    &  CAF      &  30 deg Fog     		& 239					& 254					& 268					& 283					\\
		7 (FSW7)    &  Water    &  30 deg Fog     		& 276					& 291					& 308					& 323					\\
		8 (FSE8)    &  CAF      &  30 deg Fog     		& 245					& 260					& 275					& 290					\\
		9 (Attic 1) &  Water    &  Straight Stream     	&						&						&						&					\\
		10 (Attic 2)&  CAF      &  Straight Stream     	& 						&						&						&					\\
		11 (FSE1)   &  Water    &  30 deg Fog  	   		& 315					& 330					& 345					& 360					\\
		12 (FSW1)   &  CAF      &  30 deg Fog  	   		& 233					& 248					& 263					& 278					\\
		13 (FSE2)   &  Water    &  30 deg Fog  	   		& 330					& 390					& 406					& 466					\\
		14 (FSW2)   &  CAF      &  30 deg Fog  	  		& 435					& 495					& 510					& 570					\\
		\noalign{\smallskip}\hline
	\end{tabular}
	\label{tab:Nozzle_Activation_Times}
\end{sidewaystable}

\subsection{Wood Fuel Package}
\label{subsec:Wood_Fuel_Package}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest11FirstSuppression}
	\caption{Test 11: Wood Fuel Package, Panel Window, Water, 30 deg Fog, 120 gpm, First Suppression}
	\label{fig:Test_11_First_Suppression}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest11SecondSuppression}
	\caption{Test 11: Wood Fuel Package, Panel Window, Water, 30 deg Fog, 120 gpm, Second Suppression}
	\label{fig:Test_11_Second_Suppression}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest12FirstSuppression}
	\caption{Test 12: Wood Fuel Package, Panel Window, CAFS, 30 deg Fog, 120 gpm/60cfm, First Suppression}
	\label{fig:Test_12_First_Suppression}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest12SecondSuppression}
	\caption{Test 12: Wood Fuel Package, Panel Window, CAFS, 30 deg Fog, 120 gpm/60cfm, Second Suppression}
	\label{fig:Test_12_Second_Suppression}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest13FirstSuppression}
	\caption{Test 13: Wood Fuel Package, Panel Window, Water, 30 deg Fog, 120 gpm, First Suppression}
	\label{fig:Test_13_First_Suppression}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest13SecondSuppression}
	\caption{Test 13: Wood Fuel Package, Panel Window, Water, 30 deg Fog, 120 gpm, Second Suppression}
	\label{fig:Test_13_Second_Suppression}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest14FirstSuppression}
	\caption{Test 14: Wood Fuel Package, Panel Window, CAFS, 30 deg Fog, 120 gpm/60cfm, First Suppression}
	\label{fig:Test_14_First_Suppression}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest14SecondSuppression}
	\caption{Test 14: Wood Fuel Package, Panel Window, CAFS, 30 deg Fog, 120 gpm/60cfm, Second Suppression}
	\label{fig:Test_14_Second_Suppression}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest1FirstSuppression}
	\caption{Test 1: Furniture Fuel Package, CAFS, 30 deg Fog, 120 gpm/60cfm, First Suppression}
	\label{fig:Test_1_First_Suppression}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest1SecondSuppression}
	\caption{Test 1: Furniture Fuel Package, CAFS, 30 deg Fog, 120 gpm/60cfm, Second Suppression}
	\label{fig:Test_1_Second_Suppression}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest2FirstSuppression}
	\caption{Test 2: Furniture Fuel Package, Water, 30 deg Fog, 120 gpm, First Suppression}
	\label{fig:Test_2_First_Suppression}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest2SecondSuppression}
	\caption{Test 2: Furniture Fuel Package, Water, 30 deg Fog, 120 gpm, Second Suppression}
	\label{fig:Test_2_Second_Suppression}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest5FirstSuppression}
	\caption{Test 5: Furniture Fuel Package, Water, 30 deg Fog, 120 gpm, First Suppression}
	\label{fig:Test_5_First_Suppression}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest5SecondSuppression}
	\caption{Test 5: Furniture Fuel Package, Water, 30 deg Fog, 120 gpm, Second Suppression}
	\label{fig:Test_5_Second_Suppression}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest6FirstSuppression}
	\caption{Test 6: Furniture Fuel Package, CAFS, 30 deg Fog, 120 gpm/60cfm, First Suppression}
	\label{fig:Test_6_First_Suppression}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest6SecondSuppression}
	\caption{Test 6: Furniture Fuel Package, CAFS, 30 deg Fog, 120 gpm/60cfm, Second Suppression}
	\label{fig:Test_6_Second_Suppression}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest7FirstSuppression}
	\caption{Test 7: Furniture Fuel Package, Water, 30 deg Fog, 120 gpm, First Suppression}
	\label{fig:Test_7_First_Suppression}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest7SecondSuppression}
	\caption{Test 7: Furniture Fuel Package, Water, 30 deg Fog, 120 gpm, Second Suppression}
	\label{fig:Test_7_Second_Suppression}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest8FirstSuppression}
	\caption{Test 8: Furniture Fuel Package, CAFS, 30 deg Fog, 120 gpm/60cfm, First Suppression}
	\label{fig:Test_8_First_Suppression}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest8SecondSuppression}
	\caption{Test 8: Furniture Fuel Package, CAFS, 30 deg Fog, 120 gpm/60cfm, Second Suppression}
	\label{fig:Test_8_Second_Suppression}
\end{figure}

@@

Smoke is Fuel. A ventilation limited (fuel rich) condition had developed prior to the failure of
the window. Oxygen depleted combustion products, containing carbon dioxide, carbon monoxide and
unburned hydrocarbons filled the rooms of the structure. Once the window failed, the fresh air provided
the oxygen needed to sustain the transition through flashover, which caused a significant increase in heat
release rate.
Venting does not always equal cooling. In this experiment, post ventilation temperatures and
heat fluxes all increased, due to the ventilation induced flashover.
Fire induced flows. Velocities within the structure exceeded 5 m/s (11 mph), just due to the fire
growth and the flow path that was set-up between the window opening and the corridor vent.
Avoid the flow path. The directional nature of the fire gas flow was demonstrated with thermal
conditions, both temperature and heat flux, which were twice as high in the “flow” portion of the
corridor as opposed to the “static” portion of the corridor. Thermal conditions in the
flow path were not consistent with firefighter survival.

@@

These experiments demonstrated the “extreme” thermal conditions that can be generated by a “simple
room and contents” fire and how these conditions can be extended along a flow path within a structure.
The experiments also provided potential guidance for firefighters as a part of a fire size up and approach
to the room of fire origin: note wind conditions in the area of the fire, look for “pulsing flames”,
examine smoke conditions around closed doors in the potential flow path, and maintain control of doors
in the flow path.

@@

\chapter{Spray Denisty Figures}
\label{app:spray_density}

@@

>>>>

\headerC{
\flushright{
Craig G. Weinschenk \\
Keith M. Stakes \\
Daniel Madrzykowski \\
{\em Fire Research Division \\
Engineering Laboratory} \\

@@

\large
\flushright{\bf National Institute of Standards and Technology Technical Note XXXX \\
Natl.~Inst.~Stand.~Technol.~Tech.~Note~XX, \pageref{LastPage} pages (August 2015) \\
% http://dx.doi.org/10.6028/NIST.TN.XXXX \\
CODEN: NTNOEF }

@@

@@

BB6        &   120              & 21            & Water  &  30$^{\circ}$ Fog   & 15                 &          \\
BB7        &   118              & 21            & Water  &  30$^{\circ}$ Fog   & 15                 &          \\
BB8        &   119              & 22            & Water  &  30$^{\circ}$ Fog   & 17                 &          \\
BB9        &   120              & 24            & Water  &  30$^{\circ}$ Fog   & 17~1/2             &          \\
BB10       &   127              & 20            & Water  &  Solid 7/8~in Slug  & 12~1/2             &          \\
BB11       &   120              & 22            & Water  &  Solid 7/8~in Slug  & 11~1/2             &          \\

@@

BB16       &   120 / 60cfm      &               & CAF    &  30$^{\circ}$ Fog   & 15                 &          \\

@@

BB19       &   120 / 60cfm      & 15            & CAF    &  30$^{\circ}$ Fog   & 15                 &          \\
BB20       &   120 / 60cfm      &               & CAF    &  30$^{\circ}$ Fog   & 17                 &          \\

@@

CS5        &   118              & 22            & Water  &  30$^{\circ}$ Fog   &                    &          \\
CS6        &   118              & 19            & Water  &  30$^{\circ}$ Fog   &                    &          \\
CS7        &   125              & 16            & Water  &  Solid 7/8~in Slug  &                    &          \\
CS7.2      &   120              & 17            & Water  &  Solid 7/8~in Slug  & 18                 &          \\
CS8        &   116              & 15            & Water  &  30$^{\circ}$ Fog   &                    &          \\
CS9        &   116              & 16            & Water  &  30$^{\circ}$ Fog   &                    &          \\

@@

After weighing each of the bins the mass of water (kg) in each bin was plotted by position to visualize the spray distribution. Figure~\ref{fig:Burn_Building_Test_1} shows that with a straight stream positioned {\bf here} the majority of the water accumulated along the north and east walls of the gas cooling room within the burn building (cf. Fig.~\ref{fig:Delaware_County,_PA_Burn_Building_Layout}). Figure~\ref{fig:Burn_Building_Test_7} shows difference a fog stream as the distribution of water is far more dispersed around the gas cooling room. The remainder of the burn building spray density figures are included in Appnedix~\ref{app:spray_density}.

@@

\section{Fire Suppression}
\label{sec:Fire_Suppression}
There were 14 suppression tests conducted in the single story purpose-built concrete structure. Four of the tests used a wood pallet fuel load (Section~\ref{sec:fire_suppression_pallet_fuel}) and the remaining tests used a fuel load comprised of typical household furnishings that included wooden wall paneling, two sofas, two overstuffed chairs, carpet, and padding (Section~\ref{sec:fire_suppression_furniture_fuel}). Ignition occurred in the rear of the single story structures and the available ventilation was both through the front doorway. For several tests a rear window was opened to provide additional ventilation (see Table~\ref{tab:Test_Descriptions}). The fires were intended to replicate room and contents fires typically seen within residential structures. Hose lines were pre-deployed with fixed nozzles set in two locations: one in the hallway on the approach to the burn room (hallway nozzle) and one just inside the burn room to the right side of the hallway (room nozzle). Each nozzle flowed 15~s of water or compressed air foam depending on the test. The hallway nozzle was intended to simulate a crew advancing into a structure towards the burn room. Suppression from this location would be in the form of gas cooling as the stream was not aimed at the seat of the fire (indirect interior attack). The room nozzle was intended to simulate a crew which had advanced into a structure, entered the fire room, positioned just to the side of the entry door, and began suppression on the seat of the fire (direct interior attack). Table~\ref{tab:Test_Descriptions} provides an overview of the suppression tests conducted.

\begin{table}[!ht]
	\centering
	\caption{Fire Suppression Test Descriptions}
	\begin{tabular}{llllll}
		\hline\noalign{\smallskip}
		Test		& Agent		& Stream				& Flow Rate			& Fuel           & Ventilation     \\
		\noalign{\smallskip}\hline\noalign{\smallskip}
		1 (FSE1)    &  CAF      &  30$^{\circ}$ Fog  	&  120~gpm/60~cfm   & Furniture      & Door            \\
		2 (FSW2)   	&  Water    &  30$^{\circ}$ Fog  	&  120~gpm    		& Furniture      & Door            \\
		3 (FSW3) 	&  CAF      &  7/8" Smooth Bore  	&  120~gpm/60~cfm   & Furniture      & Door            \\
		4 (FSE4)    &  Water    &  7/8" Smooth Bore  	&  120~gpm    		& Furniture      & Door            \\
		5 (FSE5)    &  Water    &  30$^{\circ}$ Fog  	&  120~gpm    		& Furniture      & Door + Window   \\
		6 (FSW6)    &  CAF      &  30$^{\circ}$ Fog  	&  120~gpm/60~cfm   & Furniture      & Door + Window   \\
		7 (FSW7)    &  Water    &  30$^{\circ}$ Fog  	&  120~gpm    		& Furniture      & Door + Window   \\
		8 (FSE8)    &  CAF      &  30$^{\circ}$ Fog  	&  120~gpm/60~cfm   & Furniture      & Door + Window   \\
		9 (Attic 1) &  Water    &  Straight Stream  	&  120~gpm    		& Furniture      & Door            \\
		10 (Attic 2)&  CAF      &  Straight Stream  	&  120~gpm/60~cfm   & Furniture      & Door            \\
		11 (FSE11)  &  Water    &  30$^{\circ}$ Fog  	&  120~gpm   		& Wood           & Door + Window   \\
		12 (FSW12)  &  CAF      &  30$^{\circ}$ Fog  	&  120~gpm/60~cfm   & Wood           & Door + Window   \\
		13 (FSE13)  &  Water    &  30$^{\circ}$ Fog  	&  120~gpm    		& Wood           & Door + Window   \\
		14 (FSW14)  &  CAF      &  30$^{\circ}$ Fog  	&  120~gpm/60~cfm   & Wood           & Door + Window   \\
		\noalign{\smallskip}\hline
	\end{tabular}
	\label{tab:Test_Descriptions}
\end{table}

@@

Figures~\ref{fig:Test_1_First_Suppression} and \ref{fig:Test_1_Second_Suppression} provide and overview of the impact of 30$^{\circ}$ fog CAF application after 15~s of application from the hallway nozzle and then 15~s of application from the room nozzle. The figures provide change in temperature and heat flux at several positions and elevations through the structure. These values are taken immediately before and after application to assess the application agent, stream, and location on interior conditions.

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest1FirstSuppression}
	\caption{Test 1: Furniture Fuel Package, CAFS, 30$^{\circ}$ Fog, 120 gpm/60cfm, First Suppression}
	\label{fig:Test_1_First_Suppression}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest1SecondSuppression}
	\caption{Test 1: Furniture Fuel Package, CAFS, 30$^{\circ}$ Fog, 120 gpm/60cfm, Second Suppression}
	\label{fig:Test_1_Second_Suppression}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest2FirstSuppression}
	\caption{Test 2: Furniture Fuel Package, Water, 30$^{\circ}$ Fog, 120 gpm, First Suppression}
	\label{fig:Test_2_First_Suppression}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest2SecondSuppression}
	\caption{Test 2: Furniture Fuel Package, Water, 30$^{\circ}$ Fog, 120 gpm, Second Suppression}
	\label{fig:Test_2_Second_Suppression}
\end{figure}

@@

Smoke is Fuel. A ventilation limited (fuel rich) condition had developed prior to the failure of the window. Oxygen depleted combustion products, containing carbon dioxide, carbon monoxide and
unburned hydrocarbons filled the rooms of the structure. Once the window failed, the fresh air provided the oxygen needed to sustain the transition through flashover, which caused a significant increase in heat release rate.

Venting does not always equal cooling. In this experiment, post ventilation temperatures and heat fluxes all increased, due to the ventilation induced flashover. Fire induced flows. Velocities within the structure exceeded 5 m/s (11 mph), just due to the fire growth and the flow path that was set-up between the window opening and the corridor vent. Avoid the flow path. The directional nature of the fire gas flow was demonstrated with thermal conditions, both temperature and heat flux, which were twice as high in the ``flow'' portion of the
corridor as opposed to the ``static" portion of the corridor. Thermal conditions in the flow path were not consistent with firefighter survival.

@@

These experiments demonstrated the ``extreme'' thermal conditions that can be generated by a ``simple room and contents'' fire and how these conditions can be extended along a flow path within a structure. The experiments also provided potential guidance for firefighters as a part of a fire size up and approach to the room of fire origin: note wind conditions in the area of the fire, look for ``pulsing flames'', examine smoke conditions around closed doors in the potential flow path, and maintain control of doors in the flow path.

@@

\chapter{Spray Density Figures}
\label{app:spray_density}

@@

\chapter{Fire Suppression Figures}
\label{app:fire_suppression}

\section{Furniture Fuel Package}
\label{appsubsec:Furniture_Fuel_Package}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest5FirstSuppression}
	\caption{Test 5: Furniture Fuel Package, Water, 30$^{\circ}$ Fog, 120 gpm, First Suppression}
	\label{fig:Test_5_First_Suppression}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest5SecondSuppression}
	\caption{Test 5: Furniture Fuel Package, Water, 30$^{\circ}$ Fog, 120 gpm, Second Suppression}
	\label{fig:Test_5_Second_Suppression}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest6FirstSuppression}
	\caption{Test 6: Furniture Fuel Package, CAFS, 30$^{\circ}$ Fog, 120 gpm/60cfm, First Suppression}
	\label{fig:Test_6_First_Suppression}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest6SecondSuppression}
	\caption{Test 6: Furniture Fuel Package, CAFS, 30$^{\circ}$ Fog, 120 gpm/60cfm, Second Suppression}
	\label{fig:Test_6_Second_Suppression}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest7FirstSuppression}
	\caption{Test 7: Furniture Fuel Package, Water, 30$^{\circ}$ Fog, 120 gpm, First Suppression}
	\label{fig:Test_7_First_Suppression}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest7SecondSuppression}
	\caption{Test 7: Furniture Fuel Package, Water, 30$^{\circ}$ Fog, 120 gpm, Second Suppression}
	\label{fig:Test_7_Second_Suppression}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest8FirstSuppression}
	\caption{Test 8: Furniture Fuel Package, CAFS, 30$^{\circ}$ Fog, 120 gpm/60cfm, First Suppression}
	\label{fig:Test_8_First_Suppression}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest8SecondSuppression}
	\caption{Test 8: Furniture Fuel Package, CAFS, 30$^{\circ}$ Fog, 120 gpm/60cfm, Second Suppression}
	\label{fig:Test_8_Second_Suppression}
\end{figure}

\section{Wood Fuel Package}
\label{appsubsec:Wood_Fuel_Package}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest11FirstSuppression}
	\caption{Test 11: Wood Fuel Package, Panel Window, Water, 30$^{\circ}$ Fog, 120 gpm, First Suppression}
	\label{fig:Test_11_First_Suppression}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest11SecondSuppression}
	\caption{Test 11: Wood Fuel Package, Panel Window, Water, 30$^{\circ}$ Fog, 120 gpm, Second Suppression}
	\label{fig:Test_11_Second_Suppression}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest12FirstSuppression}
	\caption{Test 12: Wood Fuel Package, Panel Window, CAFS, 30$^{\circ}$ Fog, 120 gpm/60cfm, First Suppression}
	\label{fig:Test_12_First_Suppression}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest12SecondSuppression}
	\caption{Test 12: Wood Fuel Package, Panel Window, CAFS, 30$^{\circ}$ Fog, 120 gpm/60cfm, Second Suppression}
	\label{fig:Test_12_Second_Suppression}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest13FirstSuppression}
	\caption{Test 13: Wood Fuel Package, Panel Window, Water, 30$^{\circ}$ Fog, 120 gpm, First Suppression}
	\label{fig:Test_13_First_Suppression}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest13SecondSuppression}
	\caption{Test 13: Wood Fuel Package, Panel Window, Water, 30$^{\circ}$ Fog, 120 gpm, Second Suppression}
	\label{fig:Test_13_Second_Suppression}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest14FirstSuppression}
	\caption{Test 14: Wood Fuel Package, Panel Window, CAFS, 30$^{\circ}$ Fog, 120 gpm/60cfm, First Suppression}
	\label{fig:Test_14_First_Suppression}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest14SecondSuppression}
	\caption{Test 14: Wood Fuel Package, Panel Window, CAFS, 30$^{\circ}$ Fog, 120 gpm/60cfm, Second Suppression}
	\label{fig:Test_14_Second_Suppression}
\end{figure}
